---
author: Eric Fay
output: pdf_document
---
# Exercises 1 - 5: Probability in R. v. Clark (Sally)
## Independent probabilities: likelihood of two deaths
Suppose the rate of sudden infant death syndrome (SIDS) is 1 in 8,500.
Define:

+ $A$ to be `Sally Clark's **first** born infant dies of SIDS'
+ $B$ to be `Sally Clark's **second** born infant dies of SIDS'

Then the probabilities for either infanty dieing of SIDS (given no additional information) are equal
$\mathbb{P}(A) = \mathbb{P}(B)$.
```{r}
P_A <- 1/8500; P_A
```
Which is a probability of approximately 0.012%.

When we know Sally's first infant dies this changes the probability of the second infant. Since we beilve SIDS has a gentic link, $A$ and $B$ are not independent. Therefore  $\mathbb{P}(A \land B) \neq \mathbb{P}(A)\cdot\mathbb{P}(B)$
and we must use conditional probability.

$$P(B|A) = \frac{\mathbb{P}(B\land A)}{\mathbb{P}(A)}$$

Assume the probibility that a child will die of SIDS given a sibling died of SIDS is $$\mathbb{P}(B|A)=\frac{1}{100}$$
```{r}
P_B_given_A <- 1/100
```
Then the probability of both infants dieing of SIDS is
$$\mathbb{P}(A\land B) = \mathbb{P}(A)\cdot\mathbb{P}(B|A)$$
```{r}
P_A_and_B <- P_A * P_B_given_A
P_A_and_B 
```

## Bayes' Theorem: Sally Clark's Murder Probability
Define these propositions to these symbols:

+ M to be 'Mother is a murder'
+ D to be 'Mother's two infants die with no evidence of harm'

To find the probability of the mother being a murder given her two childern died with no evidence of harm can be found by Bayes' Theorem.
$$\mathbb{P}(M|D)=\frac{\mathbb{P}(D|M)\cdot\mathbb{P}(M)}{\mathbb{P}(D)}$$

Suppose the probability of a murder finding a way to kill two of her infants without leaving evidence of physical harm is 50%. 
Then $$\mathbb{P}(D|M)=0.5$$
```{r}
P_D_given_M <- 0.5
```
Assume the murder rate among mother is 1 in 1 million.
$$\mathbb{P}(M)=10^{-6}$$
```{r}
P_M <- 1/1000000
```

From the previous section proposition $D$ is the same as $A\land B$ so $\mathbb{P}(D) = \mathbb{P}(A)\cdot\mathbb{P}(B|A)$.
```{r}
P_D <- P_A_and_B
```

Therefore by Bayes' Theorem
```{r}
P_M_given_D <- P_D_given_M * P_M / P_D
P_M_given_D
```
Therefore given our assumptions:

+ SIDS is genetic; $\mathbb{P}(B|A) = \frac{1}{100}$
+ There is a 50% she could kill two infants with no evidence of harm;
$\mathbb{P}(D|M)=0.5$
+ The murder rate for mothers is 1 in 1 million;
$\mathbb{P}(M)=\frac{1}{1000000}$

The probability Sally Clark kill both her children is about 43%.
